EuringPosterFigures

### 2021-08-17 figures/PaperFigures.Rmd

all.meds <- read.csv(file = here::here('results', 'Processed csvs', 'all.meds.csv'), 
                     header = T, stringsAsFactors = F)

##bias
rel.bias <- all.meds %>%
  transform(p.surv.true = ifelse(det.abund == 'L', 0.3))
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true) %>%
  dplyr::select('lambda.scenario', 'scenario',
                'phi1.bias', 'phiad.bias', 'fec.bias', 'det.MR', 'det.abund', 'det.prod') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'det.MR', 'det.abund', 'det.prod')) %>%
  group_by(lambda.scenario, det.MR, det.abund, det.prod, variable) %>%
  dplyr::summarize(bias = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>%
  transform(lambda.scenario = factor(lambda.scenario,
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(det.MR = factor(det.MR, levels = c('L', 'M', 'H'))) %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(det.prod = factor(det.prod, levels = c('L', 'M', 'H'))) %>%
  transform(missing.MR = ifelse(is.na(det.MR), 1, 0),
            missing.prod = ifelse(is.na(det.prod), 1, 0)) %>%
  transform(num.miss = missing.MR + missing.prod) %>%
  transform(dataset = ifelse(is.na(det.MR)&!is.na(det.prod), 'Counts+Prod', 
                             ifelse(!is.na(det.MR)&is.na(det.prod), 'Counts+MR',
                                    ifelse(is.na(det.MR)&is.na(det.prod), 'Counts', 'Full'))))

@@

###average over two layers of detection (det.MR and det.prod)
rel.bias.few <- rel.bias %>%
  group_by(variable, det.abund, lambda.scenario, dataset) %>%
  dplyr::summarize(bias = mean(bias), .groups = 'keep') %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(lambda.scenario = factor(lambda.scenario, 
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(dataset = factor(dataset, levels = c('Full', 'Counts+Prod', 'Counts+MR', 'Counts'),
                             labels = c('Full', 'Counts+Prod', 'Counts+MR', 'Counts')))

#use me fig 1
ggplot(rel.bias.few, aes(x = factor(det.abund), y = variable, fill = bias)) +
  geom_tile(color = 'grey50') +
  xlab('Count detection') + ylab('') +
  facet_grid(dataset ~ lambda.scenario, drop = T, scales = 'free_x', labeller = label_parsed) +
  scale_fill_gradient2(name = "Relative bias",
                     # mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0) +
                       mid = "white", low = rainbow2[2], high = rainbow2[6], midpoint = 0) +
                      # breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
 # scale_x_discrete(labels = c(expression(paste("low ", italic(p))), 
 #                             expression(paste("med ", italic(p))), 
 #                             expression(paste("high ", italic(p))))) +
  theme_light() +
  theme(legend.position = 'top',
        # axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
        # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line"))

@@

ggplot(rel.bias.few, aes(x = det.abund, y = bias, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('Count detection') + ylab('Relative bias') +
  facet_grid(dataset~lambda.scenario, scales = 'free_x') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')

@@

## dot plot
# ggplot(plot.vals, aes(x = fec_cat, y = value, col = factor(dataset), group = factor(dataset))) +
#   geom_point() + geom_line() +
#   geom_hline(aes(yintercept = 0), linetype = 'dotted') +
#   xlab('True fecundity') + ylab('Relative bias') +
#   facet_grid(variable~phi1_cat, scales = 'free') +
#   theme_bw() +
#   theme(legend.position = 'top',
#              plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
#   scale_color_manual(values = rainbow2[-c(1,4)], name = '')

ggplot(plot.vals, aes(x = fec_cat, y = value, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('True fecundity') + ylab('Relative bias') +
  facet_grid(dataset~phi1_cat, scales = 'free_x') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')

@@

#for the love of buddha, someone please check this calculation of rmse
rmse.vals <- all.meds %>%
  transform(fec.rmse = (fec.obs-fec.true)^2,
            phiad.rmse = (phiad.obs-phiad.true)^2,
            phi1.rmse = (phi1.obs-phi1.true)^2) %>%
  dplyr::select(lambda.scenario, scenario, fec.rmse, phiad.rmse, phi1.rmse, 
                det.MR, det.abund, det.prod) %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'det.MR', 'det.abund', 'det.prod')) %>%
  group_by(lambda.scenario, det.MR, det.abund, det.prod, variable) %>%
  dplyr::summarize(mean.rmse = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.rmse', 'phi1.rmse', 'fec.rmse'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>%
  transform(lambda.scenario = factor(lambda.scenario,
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(det.MR = factor(det.MR, levels = c('L', 'M', 'H'))) %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(det.prod = factor(det.prod, levels = c('L', 'M', 'H'))) %>%
  transform(missing.MR = ifelse(is.na(det.MR), 1, 0),
            missing.prod = ifelse(is.na(det.prod), 1, 0)) %>%
  transform(num.miss = missing.MR + missing.prod) %>%
  transform(dataset = ifelse(is.na(det.MR)&!is.na(det.prod), 'Counts+Prod', 
                             ifelse(!is.na(det.MR)&is.na(det.prod), 'Counts+MR',
                                    ifelse(is.na(det.MR)&is.na(det.prod), 'Counts', 'Full'))))

@@

#use me fig 3
ggplot(rmse.few, aes(x = factor(det.abund), y = variable, fill = rmse)) +
  geom_tile(color = 'grey50') +
  xlab('Count detection') + ylab('') +
  facet_grid(dataset ~ lambda.scenario, drop = T, scales = 'free_x', labeller = label_parsed) +
  scale_fill_gradient2(name = "RMSE",
                       mid = "white", high = rainbow2[2], midpoint = 0) +
                      # breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
 # scale_x_discrete(labels = c(expression(paste("low ", italic(p))), 
 #                             expression(paste("med ", italic(p))), 
 #                             expression(paste("high ", italic(p))))) +
  theme_light() +
  theme(legend.position = 'top',
        # axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
        # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line"))

@@

ggplot(rmse.few, aes(x = det.abund, y = rmse, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('Count detection') + ylab('RMSE') +
  facet_grid(dataset~lambda.scenario, scales = 'free') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')

@@

#use me fig 3
ggplot(plot.vals.rmse, aes(x = factor(fec_cat), y = factor(variable), fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True fecundity') + ylab('') +
  facet_grid(dataset~phi1_cat, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "RMSE",
                      mid = "white", high = rainbow2[2], midpoint = 0,
                      # breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_light() +
  theme(legend.position = 'top',
        # axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
        # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line"))

>>>>

all.meds <- read.csv(file = here::here('figures', 'Processed csvs', 'all.meds.csv'), 
                     header = T, stringsAsFactors = F)

##bias
rel.bias <- all.meds %>%
  transform(p.surv.true = ifelse(det.abund == 'L', 0.3, 
            ifelse(det.abund == 'M', 0.5, 
                   ifelse(det.abund == 'H', 0.8, NA)))) %>%
  transform(mean.p.true = ifelse(det.MR == 'L', 0.3, 
            ifelse(det.MR == 'M', 0.5, 
                   ifelse(det.MR == 'H', 0.8, NA)))) %>%
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true,
            p.surv.bias = (p.surv-p.surv.true)/p.surv.true,
            mean.p.bias = (mean.p-mean.p.true)/mean.p.true) %>%
  dplyr::select('lambda.scenario', 'scenario',
                'phi1.bias', 'phiad.bias', 'fec.bias', 'det.MR', 'det.abund', 'det.prod', 'mean.p.bias', 'p.surv.bias') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'det.MR', 'det.abund', 'det.prod')) %>%
  group_by(lambda.scenario, det.MR, det.abund, det.prod, variable) %>%
  dplyr::summarize(bias = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias', 'p.surv.bias', 'mean.p.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity', 'Count detection', 'Resight detection'))) %>%
  transform(lambda.scenario = factor(lambda.scenario,
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(det.MR = factor(det.MR, levels = c('L', 'M', 'H'))) %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(det.prod = factor(det.prod, levels = c('L', 'M', 'H'))) %>%
  transform(missing.MR = ifelse(is.na(det.MR), 1, 0),
            missing.prod = ifelse(is.na(det.prod), 1, 0)) %>%
  transform(num.miss = missing.MR + missing.prod) %>%
  transform(dataset = ifelse(is.na(det.MR)&!is.na(det.prod), 'Counts+Prod', 
                             ifelse(!is.na(det.MR)&is.na(det.prod), 'Counts+MR',
                                    ifelse(is.na(det.MR)&is.na(det.prod), 'Counts', 'Full'))))

@@

###average over two layers of detection (det.MR and det.prod)
obs.pars <- c('Resight detection', 'Count detection')
rel.bias.few <- rel.bias %>%
  group_by(variable, det.abund, lambda.scenario, dataset) %>%
  dplyr::summarize(bias = mean(bias), .groups = 'keep') %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(lambda.scenario = factor(lambda.scenario, 
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(dataset = factor(dataset, levels = c('Full', 'Counts+Prod', 'Counts+MR', 'Counts'),
                             labels = c('Full', 'Counts+Prod', 'Counts+MR', 'Counts')))

#heat tiles
# ggplot(rel.bias.few %>% filter(variable %nin% obs.pars), 
#        aes(x = factor(det.abund), y = variable, fill = bias)) +
#   geom_tile(color = 'grey50') +
#   xlab('Count detection') + ylab('') +
#   facet_grid(dataset ~ lambda.scenario, drop = T, scales = 'free_x', labeller = label_parsed) +
#   scale_fill_gradient2(name = "Relative bias",
#                      # mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0) +
#                        mid = "white", low = rainbow2[2], high = rainbow2[6], midpoint = 0) +
#                       # breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
#  # scale_x_discrete(labels = c(expression(paste("low ", italic(p))), 
#  #                             expression(paste("med ", italic(p))), 
#  #                             expression(paste("high ", italic(p))))) +
#   theme_light() +
#   theme(legend.position = 'top',
#         # axis.text.y = element_blank(),
#         axis.ticks.y = element_blank(),
#         axis.ticks.x = element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         strip.text = element_text(face = "bold", color = "black"),
#         strip.background = element_rect(fill = NA, color = "black"),
#         axis.text.x = element_text(angle = 0, vjust = 1.5),
#         # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
#         panel.border = element_rect(color = "black", fill = NA),  
#         panel.spacing.x = unit(0.75, "line"))

@@

#use me fig 1a
pdf(here("figures", "bias.lambda.ecol.pdf"), width = 8, height = 12)
ggplot(rel.bias.few  %>% filter(variable %nin% obs.pars), 
       aes(x = det.abund, y = bias, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('Count detection') + ylab('Relative bias') +
  facet_grid(dataset~lambda.scenario, scales = 'free_x') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')
dev.off()

#use me fig 1b
pdf(here("figures", "bias.lambda.obs.pdf"), width = 8, height = 12)
ggplot(rel.bias.few  %>% filter(variable %in% obs.pars), 
       aes(x = det.abund, y = bias, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('Count detection') + ylab('Relative bias') +
  facet_grid(dataset~lambda.scenario, scales = 'free_x') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')
dev.off()

@@

## dot plot
#use me figure 2
pdf(here("figures", "bias.dem.ecol.pdf"), width = 8, height = 12)
ggplot(plot.vals, aes(x = fec_cat, y = value, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('True fecundity') + ylab('Relative bias') +
  facet_grid(dataset~phi1_cat, scales = 'free_x') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')
dev.off()

@@

#for the love of buddha, someone please check this calculation of rmse
rmse.vals <- all.meds %>%
  transform(p.surv.true = ifelse(det.abund == 'L', 0.3, 
            ifelse(det.abund == 'M', 0.5, 
                   ifelse(det.abund == 'H', 0.8, NA)))) %>%
  transform(mean.p.true = ifelse(det.MR == 'L', 0.3, 
            ifelse(det.MR == 'M', 0.5, 
                   ifelse(det.MR == 'H', 0.8, NA)))) %>%
  transform(fec.rmse = (fec.obs-fec.true)^2,
            phiad.rmse = (phiad.obs-phiad.true)^2,
            phi1.rmse = (phi1.obs-phi1.true)^2,
            mean.p.rmse = (mean.p-mean.p.true)^2,
            p.surv.rmse = (p.surv-p.surv.true)^2) %>%
  dplyr::select(lambda.scenario, scenario, fec.rmse, phiad.rmse, phi1.rmse, p.surv.rmse, mean.p.rmse,
                det.MR, det.abund, det.prod) %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'det.MR', 'det.abund', 'det.prod')) %>%
  group_by(lambda.scenario, det.MR, det.abund, det.prod, variable) %>%
  dplyr::summarize(mean.rmse = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.rmse', 'phi1.rmse', 'fec.rmse', 
                                                   'p.surv.rmse', 'mean.p.rmse'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity',
                                         'Count detection', 'Resight detection'))) %>%
  transform(lambda.scenario = factor(lambda.scenario,
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(det.MR = factor(det.MR, levels = c('L', 'M', 'H'))) %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(det.prod = factor(det.prod, levels = c('L', 'M', 'H'))) %>%
  transform(missing.MR = ifelse(is.na(det.MR), 1, 0),
            missing.prod = ifelse(is.na(det.prod), 1, 0)) %>%
  transform(num.miss = missing.MR + missing.prod) %>%
  transform(dataset = ifelse(is.na(det.MR)&!is.na(det.prod), 'Counts+Prod', 
                             ifelse(!is.na(det.MR)&is.na(det.prod), 'Counts+MR',
                                    ifelse(is.na(det.MR)&is.na(det.prod), 'Counts', 'Full'))))

@@

#use me fig 3
pdf(here("figures", "rmse.lambda.ecol.pdf"), width = 8, height = 12)
ggplot(rmse.few %>% filter(variable %nin% obs.pars), aes(x = factor(det.abund), y = variable, fill = rmse)) +
  geom_tile(color = 'grey50') +
  xlab('Count detection') + ylab('') +
  facet_grid(dataset ~ lambda.scenario, drop = T, scales = 'free_x', labeller = label_parsed) +
  scale_fill_gradient2(name = "RMSE",
                       mid = "white", high = rainbow2[2], midpoint = 0) +
                      # breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
 # scale_x_discrete(labels = c(expression(paste("low ", italic(p))), 
 #                             expression(paste("med ", italic(p))), 
 #                             expression(paste("high ", italic(p))))) +
  theme_light() +
  theme(legend.position = 'top',
        # axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
        # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line"))
dev.off()

pdf(here("figures", "rmse.lambda.obs.pdf"), width = 8, height = 12)
ggplot(rmse.few %>% filter(variable %in% obs.pars), aes(x = factor(det.abund), y = variable, fill = rmse)) +
  geom_tile(color = 'grey50') +
  xlab('Count detection') + ylab('') +
  facet_grid(dataset ~ lambda.scenario, drop = T, scales = 'free_x', labeller = label_parsed) +
  scale_fill_gradient2(name = "RMSE",
                       mid = "white", high = rainbow2[2], midpoint = 0) +
                      # breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
 # scale_x_discrete(labels = c(expression(paste("low ", italic(p))), 
 #                             expression(paste("med ", italic(p))), 
 #                             expression(paste("high ", italic(p))))) +
  theme_light() +
  theme(legend.position = 'top',
        # axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
        # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line"))
dev.off()

@@

ggplot(rmse.few %>% filter(variable %nin% obs.pars), aes(x = det.abund, y = rmse, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('Count detection') + ylab('RMSE') +
  facet_grid(dataset~lambda.scenario, scales = 'free') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')

ggplot(rmse.few %>% filter(variable %in% obs.pars), aes(x = det.abund, y = rmse, col = factor(variable), group = factor(variable))) +
  geom_point() + geom_line() +
  geom_hline(aes(yintercept = 0), linetype = 'dotted') +
  xlab('Count detection') + ylab('RMSE') +
  facet_grid(dataset~lambda.scenario, scales = 'free') +
  theme_bw() +
  theme(legend.position = 'top',
             plot.subtitle = element_text(size = 10, hjust = 0.5, vjust = 1)) +
  scale_color_manual(values = rainbow2[-c(1,4)], name = '')

@@

#use me fig 3
pdf(here("figures", "rmse.dem.ecol.pdf"), width = 8, height = 12)
ggplot(plot.vals.rmse, aes(x = factor(fec_cat), y = factor(variable), fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True fecundity') + ylab('') +
  facet_grid(dataset~phi1_cat, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "RMSE",
                      mid = "white", high = rainbow2[2], midpoint = 0,
                      # breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_light() +
  theme(legend.position = 'top',
        # axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
        # ggh4x.facet.nestline = element_line(size = 0.5), #what does this line do?
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line"))
dev.off()
